Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-06-09 WSSSPE1_report/WSSSPE1_summary_report.tex
Made it clearer that this refers to the earl years of development
Review queried tapes with regards to GCC, Emacs etc as they are still
developed today. Made the sentence more complete, making it clear that
this simply refers to their early development (not the present day,
where they also benefit from immediate sharing).

It appears that while some of the basics of computing may be
similar, the tools commonly used for computing have changed quite
significantly. Reference was made to Perl, which was commonly used,
giving way to whole new languages, such as Python, for gluing things
together and how this induces many students into entirely rewriting
the scaffolding, leaving the old to rot and the experiments to become
non-reproducible as the tools change. There was discussion of this
tendency along with the enormous differences in the speed and ease of
sharing---having to ship tapes around (GCC, Emacs, etc) as opposed to
the immediate sharing of the latest development online, using revision
control systems like CVS, Subversion, Git, Mercurial, Bazaar, etc.

>>>>

It appears that while some of the basics of computing may be
similar, the tools commonly used for computing have changed quite
significantly. Reference was made to Perl, which was commonly used,
giving way to whole new languages, such as Python, for gluing things
together and how this induces many students into entirely rewriting
the scaffolding, leaving the old to rot and the experiments to become
non-reproducible as the tools change. There was discussion of this
tendency along with the enormous differences in the speed and ease of
sharing---having to ship tapes around in the early days of software development
(shapnig development of GCC, Emacs, in their formative years) as opposed to
the immediate sharing of the latest development online, using revision
control systems like CVS, Subversion, Git, Mercurial, Bazaar, etc.
